
\documentclass[conference]{IEEEtran}
% \documentclass[conference]{IEEEtran
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{algorithmic}
\usepackage{graphicx} 
\graphicspath{ {./pics/} }
\usepackage{subfig}
\usepackage{wrapfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% This is to include code
\usepackage{listings}
\usepackage{xcolor}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstdefinestyle{Python}{
    language        = Python,
    basicstyle      = \ttfamily,
    keywordstyle    = \color{blue},
    keywordstyle    = [2] \color{teal},
    stringstyle     = \color{green},
    commentstyle    = \color{red}\ttfamily
}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{reflection}[2][Reflection]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{proposition}[2][Proposition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\begin{document}

% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------

\title{MIALab Project HS2020}

\author{\IEEEauthorblockN{1\textsuperscript{st} Thomas Buchegger}
\IEEEauthorblockA{\textit{University of Bern} \\
Bern, Switzerland \\
thomas.buchegger@students.unibe.ch}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Carolina Duran}
\IEEEauthorblockA{\textit{University of Bern} \\
Bern, Switzerland \\
carolina.duran@students.unibe.ch}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Stefan Weber}
\IEEEauthorblockA{\textit{University of Bern} \\
Bern, Switzerland \\
stefan.weber@students.unibe.ch}
}
\date{03.06.2020}

\maketitle



% --------------------------------------------------------------
% Abstract
% --------------------------------------------------------------

\newpage

\begin{abstract}
Here is the abstract


\end{abstract}

\newpage

% --------------------------------------------------------------
% Introduction
% --------------------------------------------------------------

\section{Introduction}

\textbf{Our hypothesis: "Image normalization has an important influence on the segmentation".
Aims of the introduction:
\begin{itemize}
\item To demonstrate importance/impact need
\item To demonstrate novelty
\item To justify the hypothesis / aims / investigated technology
\item To establish expectations/scope of the report
\end{itemize} 
Some questions which could be answered:
Currently, z score normalization is implemented.
\begin{itemize}
\item Are there more powerful normalization methods?
\item Is normalization really needed?
\item Is the provided data already normalized in some way?
\item Can you also unnormalize data to show a negative effect?
\end{itemize}
For the research:
\begin{itemize}
\item Understand the problem
\item What have others already done / is there already a solution?
\item Can I apply a solution to another problem to my problem?
\item What lessons can I learn from others work?
\item What deficiencies exist in others work?
\end{itemize}
\begin{enumerate}
\item Demonstrate importance
	\begin{enumerate}
	\item Define the problem
	\item Explain the criticality, impact of the problem
	\end{enumerate}
\item Demonstrate Novelty
	\begin{enumerate}
	\item Explain what is the state of the art / current practice
	\item Explain what preliminary / related work has been done towards solving the problem by you and others
	\item Explain what deficiencies / problems still exist (specifically the one that you will try to address)
	\end{enumerate}
\item Present and Justify the Hypothesis / aim / objective
	\begin{enumerate}
	\item State Hypothesis /aim/ objective
	\item Describe evidence supporting hypothesis
	\end{enumerate}
\item Establish expectations of the report
	\begin{enumerate}
	\item Describe scope of the presented work
	\item Present a summary of remainder of the report
	\end{enumerate}
\end{enumerate} 
}


\section{Methodology}


\subsection{Data}
\subsection{Evaluation}

\section{Results}
\textbf{The results section should match approximately the data analysis section.}\\


\section{Discussion}
\textbf{Aims of the Discussion part:
\begin{itemize}
\item Highlight importance of your work (highlight novelty /impact etc
\item To interpret your results in relation to your original problem
\item To put your work into the context of existing work
\item To present any limitations of the presented work
\item To make future recommendations
\item To provide a conclusion of the work
\end{itemize}
\begin{enumerate}
\item Importance of the work
	\begin{enumerate}
	\item Summarise your results
	\item Reiterate the importance of the work (novelty , impact etc)
	\end{enumerate}
\item Interpretation of results
	\begin{enumerate}
	\item Interpret your results focussing on the problem described in the introduction. What do the results mean for the described problem?
	\item Explain any unusual/important findings (be careful if not your original investigative subject)
	\end{enumerate}
\item Provide context
	\begin{enumerate}
	\item Describe your results in relation to others and try to explain any discrepancies
	\item Emphasize how your results support or refute your hypotheses current thinking in the field. Were results as expected? If not why and what does this mean?
	\end{enumerate}
\item Limitations of your work
	\begin{enumerate}
	\item Describe any limitations /deficiencies of your work and what impact they have on the findings
	\item Suggest possible future solutions
	\end{enumerate}
\item Conclusions
	\begin{enumerate}
	\item Summarise your findings and relate your findings back to your hypothesis / aim / objective and to your problem.
	\item Based on your findings, suggest next steps towards solving your problem
	\end{enumerate}
\end{enumerate} 
}

\section*{Acknowledgment}

\pagebreak
\begin{thebibliography}{00}
    \bibitem{b1} Test reference 1
    \bibitem{b2} Test reference 2
\end{thebibliography}
\end{document}
